```{r library, include=FALSE}
my_packages <- c("tidyverse", "data.table",
                 "stringdist")
pacman::p_load(char = my_packages)

tmp <- list()
```

Each drug test platform has its own name system which may induce name duplication.

# Load data
```{r}
load(file = "Output/01/drug.Rda")
load(file = "Output/01/drug_anno.Rda")
```

# CCLE anno
```{r}
ccle_drug_anno <- fread("Input/Raw/DrugAnno/Repurposing_Hub_export.txt")
ccle_drug_anno$Name <- toupper(ccle_drug_anno$Name)
```

# Rename gdsc
GDSC anno file `DRUG_NAME2` col will be used as concensus drug name.
We will rename drug name in gdsc1/2 to be corresponded with gdsc anno file. 

GDSC1:
```{r}
tmp_df <- merge(
  data.frame(
    old = rownames(gdsc1_drug)
  ), gdsc_drug_anno2[,c(1,6)], by = "old", all.x = T
) %>% unique()
tmp_df <- tmp_df[match(rownames(gdsc1_drug), tmp_df$old),]
rownames(gdsc1_drug)[!is.na(tmp_df$DRUG_NAME2)] <- tmp_df$DRUG_NAME2[!is.na(tmp_df$DRUG_NAME2)]

table(rownames(gdsc1_drug) %in% gdsc_drug_anno2$DRUG_NAME2)
```

GDSC2:
```{r}
tmp_df <- merge(
  data.frame(
    old = rownames(gdsc2_drug)
  ), gdsc_drug_anno2[,c(1,6)], by = "old", all.x = T
) %>% unique()
tmp_df <- tmp_df[match(rownames(gdsc2_drug), tmp_df$old),]
rownames(gdsc2_drug)[!is.na(tmp_df$DRUG_NAME2)] <- tmp_df$DRUG_NAME2[!is.na(tmp_df$DRUG_NAME2)]

table(rownames(gdsc2_drug) %in% gdsc_drug_anno2$DRUG_NAME2)
```

```{r}
cat(rownames(gdsc2_drug)[!rownames(gdsc2_drug) %in% gdsc_drug_anno2$DRUG_NAME2],
    sep = ", ")
```


```{r}
gdsc_drug_anno3 <- unique(gdsc_drug_anno2[,-c(2,6)])
colnames(gdsc_drug_anno3)[1] <- "DRUG_NAME"

# gdsc_drug_anno2 <- fread("Input/Raw/DrugAnno/gdsc_screened_compounds_rel_8.4.csv")
# gdsc_drug_anno2 <- unique(gdsc_drug_anno2[,-c(1:2)])
# gdsc_drug_anno2$DRUG_NAME <- toupper(gdsc_drug_anno2$DRUG_NAME)
gdsc_drug_anno <- gdsc_drug_anno3
```

# Basic fix
```{r}
# basicFixName <- function(df){
#   rownames(df) <- toupper(rownames(df))
#   rownames(df) <- gsub("-", "", rownames(df))
#   rownames(df) <- gsub(" ", "", rownames(df))
#   return(df)
# }
```

```{r}
tmp$list <- list(
  ctrp1 = rownames(ctrp1_drug),
  ctrp2 = rownames(ctrp2_drug),
  prism = rownames(prism_drug),
  gCSI = rownames(gCSI_drug)
)
```

```{r}
rownames(ctrp1_drug) <- toupper(rownames(ctrp1_drug))
rownames(ctrp2_drug) <- toupper(rownames(ctrp2_drug))
rownames(prism_drug) <- toupper(rownames(prism_drug))
rownames(gCSI_drug) <- toupper(rownames(gCSI_drug))
```

# Remove duplicate
```{r}
drug_names <- unique(
              c(rownames(gdsc1_drug), 
                rownames(gdsc2_drug),
                rownames(prism_drug)
                )
              )
```


```{r}
all_drug_df <- data.frame(
  drugs = c(rownames(ctrp1_drug),rownames(ctrp2_drug), rownames(prism_drug),
            rownames(gCSI_drug), rownames(gdsc1_drug),
            rownames(gdsc2_drug)),
  type = c(rep("ctrp1", nrow(ctrp1_drug)),
           rep("ctrp2", nrow(ctrp2_drug)),
           rep("prism", nrow(prism_drug)),
           rep("gCSI", nrow(gCSI_drug)),
           rep("gdsc1", nrow(gdsc1_drug)),
           rep("gdsc2", nrow(gdsc2_drug))
           )
)
all_drug_df2 <- data.frame(drugs = unique(all_drug_df$drugs),
                           index = as.character( 1:length(unique(all_drug_df$drugs))))
```

## stringdist
```{r}
all_drug_dist_df1 <- stringdistmatrix(
  all_drug_df2$drugs, all_drug_df2$drugs, method = "osa"
)
# all_drug_dist_df2 <- stringdistmatrix(
#   all_drug_df2$drugs, all_drug_df2$drugs, method = "lv"
# )
# all_drug_dist_df3 <- stringdistmatrix(
#   all_drug_df2$drugs, all_drug_df2$drugs, method = "hamming"
# )

# all_drug_dist_df1_1 <- as.data.frame(all_drug_dist_df1)

all_drug_dist_df1_sel <- all_drug_dist_df1 < 2 & all_drug_dist_df1 > 0
```

Set triangle matrix to remove duplicates:
```{r}
upper <- which(upper.tri(all_drug_dist_df1_sel), arr.ind = TRUE)
all_drug_dist_df1_sel[upper] <- F
```


```{r}
simi_drug <- list()
for(x in 1:ncol(all_drug_dist_df1_sel)){
  index1 = x
  index2 = which(all_drug_dist_df1_sel[,x])
  simi_drug[[x]] <- c(all_drug_df2$drugs[index1],
                      all_drug_df2$drugs[index2])
}
simi_drug2 <- simi_drug[which(sapply(simi_drug, length) > 1)]

a <- sapply(simi_drug2, function(x){sum(grepl("-",x)) == 1})
simi_drug3 <- simi_drug2[a]
```

## Rename
If name in gdsc_drug_anno, then the name in ccle_drug_anno and drug files will be renamed. Then in ccle_drug_anno, rename it. Then in gdsc drug files, then name it. Lastly, follow the major name.
```{r}
for(i in simi_drug3){
  # i = simi_drug3[[1]]
  a1 <- colSums(sapply(i, function(x){grepl(x, gdsc_drug_anno$DRUG_NAME)}))
  a2 <- colSums(sapply(i, function(x){grepl(x , ccle_drug_anno$Name)}))
  if(sum(a1) > 0){
    a22 <- names(a2)[which(as.logical(a2))]
    a23 <- names(a2)[which(as.logical(a1))]
    # Rename ccle anno
    ccle_drug_anno$Name[ccle_drug_anno$Name %in% a22] <- a23
    # Rename drugs
    rownames(ctrp1_drug)[rownames(ctrp1_drug) %in% a22] <- a23
    rownames(ctrp2_drug)[rownames(ctrp2_drug) %in% a22] <- a23
    rownames(prism_drug)[rownames(prism_drug) %in% a22] <- a23
    rownames(gCSI_drug)[rownames(gCSI_drug) %in% a22] <- a23
    rownames(gdsc1_drug)[rownames(gdsc1_drug) %in% a22] <- a23
    rownames(gdsc2_drug)[rownames(gdsc2_drug) %in% a22] <- a23
  } else if (sum(a2) > 0) {
    a22 <- names(a2)[which(!as.logical(a2))]
    a23 <- names(a2)[which(as.logical(a2))]
    # Rename drugs
    rownames(ctrp1_drug)[rownames(ctrp1_drug) %in% a22] <- a23
    rownames(ctrp2_drug)[rownames(ctrp2_drug) %in% a22] <- a23
    rownames(prism_drug)[rownames(prism_drug) %in% a22] <- a23
    rownames(gCSI_drug)[rownames(gCSI_drug) %in% a22] <- a23
    rownames(gdsc1_drug)[rownames(gdsc1_drug) %in% a22] <- a23
    rownames(gdsc2_drug)[rownames(gdsc2_drug) %in% a22] <- a23
  } else {
    # 
  }
}
```

## check rename
```{r}
all_drug_df2 <- data.frame(
  drugs = c(rownames(ctrp1_drug),rownames(ctrp2_drug), rownames(prism_drug),
            rownames(gCSI_drug), rownames(gdsc1_drug),
            rownames(gdsc2_drug)),
  type = c(rep("ctrp1", nrow(ctrp1_drug)),
           rep("ctrp2", nrow(ctrp2_drug)),
           rep("prism", nrow(prism_drug)),
           rep("gCSI", nrow(gCSI_drug)),
           rep("gdsc1", nrow(gdsc1_drug)),
           rep("gdsc2", nrow(gdsc2_drug))
           )
)
# all_drug_df2 <- data.frame(drugs = unique(all_drug_df$drugs),
#                            index = as.character( 1:length(unique(all_drug_df$drugs))))
```

# Rescale drugs
lower metric means higher sensitivity.

Follow the less change principle:
```{r}
gCSI_drug2 <- as.matrix(gCSI_drug)
# gCSI_drug2[gCSI_drug2 %in% 0] <- NA
gCSI_drug2 <- apply(gCSI_drug2, 2, function(x){
    tmp <- -x
    tmp <- tmp - min(tmp, na.rm = T)
  })
gCSI_drug <- as.data.frame(gCSI_drug2)
```
gCSI_drug AAC >> -x - min(-x)

# Rename drugs
```{r}
rownames(gdsc1_drug)[rownames(gdsc1_drug) %in% "SEPANTRONIUM BROMIDE"] <- "YM-155"
rownames(gdsc2_drug)[rownames(gdsc2_drug) %in% "SEPANTRONIUM BROMIDE"] <- "YM-155"
```


# Others
```{r}
# ccle_drug_anno$Name <- gsub("-", "", ccle_drug_anno$Name)
# ccle_drug_anno$Name <- gsub(" ", "", ccle_drug_anno$Name)
```

```{r}
table(rownames(ctrp1_drug) %in% ccle_drug_anno$Name)

# table(tmp$list$ctrp1 %in% ccle_drug_anno$Name)
```

```{r}
# fwrite(gdsc_drug_anno, file = "Tmpout/tmp/gdsc_drug_anno.csv")
# fwrite(ccle_drug_anno, file = "Tmpout/tmp/ccle_drug_anno.csv")
```

## Check cell names
```{r}
all_cell_df2 <- data.frame(
  cells = c(colnames(ctrp1_drug),colnames(ctrp2_drug), colnames(prism_drug),
            colnames(gCSI_drug), colnames(gdsc1_drug),
            colnames(gdsc2_drug)),
  type = c(rep("ctrp1", ncol(ctrp1_drug)),
           rep("ctrp2", ncol(ctrp2_drug)),
           rep("prism", ncol(prism_drug)),
           rep("gCSI", ncol(gCSI_drug)),
           rep("gdsc1", ncol(gdsc1_drug)),
           rep("gdsc2", ncol(gdsc2_drug))
           )
)
```

# Save
Resave formatted and renamed drug mtx and drug anno df:
```{r}
save(
  gdsc_drug_anno,
  ccle_drug_anno,
  file = "Output/02/drug_anno.Rda"
)

save(
  prism_drug,
  ctrp1_drug,
  ctrp2_drug,
  gCSI_drug,
  gdsc1_drug,
  gdsc2_drug,
  file = "Output/02/drug2.Rda"
)
```

